---
title: "Marketing Report"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(ggplot2)
library(formatR)
library(tidyverse)
library(knitr)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(htmltools.dir.version = FALSE)
```

# Description


`r newthought('Within the Encoura Data Lab tool')` we get access to data on student sentiment regarding marketing in higher education. 

In order to make use of this information, I have been putting together a report that builds a persona of the students most likely to enroll at USM. 

To do this, I had a discussion with our NRCCUA representative, Patricia Plourde. She urged me to make use of the Encoura data download of names we have purchased since the Data Lab platform went live in July 2019. In that dataset, each student is assigned a value that corresponds to one of the 6 student mindsets as defined in their documentation.   \href{https://encoura.org/prospective-student-mindsets/}{{\color{blue}{\underline{The definitions are linked here.}}}} The data provided at this link is also pasted into this report. 


# Findings

Because the mindset data has only been available to us since July, 2019, we are limited to the few records of applicants who have a mindset value assigned. We have 61 students who applied from the NRCCUA Seniors purchase. The mindset breakdown is shown below.  

```{r}
Data_1 <- read.csv("C:/Users/christine.iyer/Box/Student_Sentiment/StudentSentiment/Data/20200423_Prospects_009762_SO-00176008_USM_Spring_2020 (1).csv", header = T, stringsAsFactors = F)

Data_2 <- read.csv("C:/Users/christine.iyer/Box/Student_Sentiment/StudentSentiment/Data/20191127_Prospects_009762_SO-00176008_FY20_Fall_Search (2).csv", header = T, stringsAsFactors = F)
Data_3 <- read.csv("C:/Users/christine.iyer/Box/Student_Sentiment/StudentSentiment/Data/20200224_Prospects_009762_SO-00176008_2020_2021_grads_winter_2_21_2020 (2).csv", header = T, stringsAsFactors = F)
```


```{r}
AllData <- rbind.data.frame(Data_3, Data_2, Data_1)
```

```{r}

SR <- AllData %>% filter (Graduation.Year == 2020)

```

```{r}
SFData <- read.csv("C:/Users/christine.iyer/Box/Student_Sentiment/StudentSentiment/Data/SFData.csv")
SFData <- SFData %>% filter(App.Application.Date != "")
```


```{r}
trythis <- merge(AllData, SFData, by = "Email" )
```

```{r}
trythis <- trythis %>% mutate(Mindset = ifelse(Mindset == 1, "Career Pragmatists", ifelse(Mindset == 2, "Career through Academics", ifelse(Mindset == 3, "Experiential Interests", ifelse(Mindset == 4, "Exploration and Meaning", ifelse(Mindset == 5, "Grad School Bound", "Social Focus"))))))
```


```{r}



kable(trythis %>%
        group_by(Mindset) %>% 
      summarise(Apps =  n(), 
                `Percent of Total` =paste0(round(100*Apps/61,0),'%')) %>% 
      arrange(desc(Apps)))
```











# __Mindsets Defined:__ 

The information below is pasted from the Encoura website. It defines the various mindsets and offers information on how best to communicate with each one. 


## __Grad School Bound__: 10% (USM 33%)

For these students, graduate or professional school is the goal. Scientific and technical skills and undergraduate research are key experiences, and academic quality and academic environment drive choice.


__The Opening Conversation__

* Show that your institution has the academics/research rigor that will land them in the graduate school of their choice
* Show evidence of successful graduate school placements 
* Demonstrate opportunities to build research skills under the guidance of faculty

__Potential Blind Spots__

* They often don’t factor affordability into the equation early on
* There is a potential impact of student loans on their future plans for graduate school
* They have less engagement with the wider opportunities of undergraduate education

__Opportunities for Support__

* Map out academic, research, and internship experiences that build grad opportunities 
* May eschew other important experiences and risk isolation or burnout as a result
* Help them understand how a more well-rounded experience will benefit them

## __Career Through Academics__: 14% (USM 21%)

These students are looking for a long-term career and see strong academics integrated with career preparation as the path. They are level-headed decision-makers.

__The Opening Conversation__

* All the major experiences of a college bear on their eventual outcome
* Show a direct connection between major and career
* Demonstrate an integrated experience of academics, career, and social interaction

__Potential Blind Spots__

* They are so focused on ultimate goal, that they might miss out on serendipitous learning 
* Show them that these experiences are not necessarily distractions, but can enrich, and enhance

__Opportunities for Support__

* Connect academic program strongly to their career goals
* If plans aren’t working out, they’ll need help finding a new focus

## __Exploration and Meaning__: 17% (USM 15%)

These students want to make an impact on the world and are wide open to liberal arts outcomes. They are global butterflies and could make an impassioned choice

__The Opening Conversation__

* Opportunities should be designed to help students make a personal impact on the world 
* Study abroad and global options will have great appeal
* They are looking for traditional liberal arts outcomes

__Potential Blind Spots__

* They give unrealistic attention to career outcomes. 
* Affordability is not top of mind
* They are at risk of making an impassioned choice without considering ROI

__Opportunities for Support__

* Coach them to direct their attention to making an impact on themselves
* Provide career advising that balances reality with exploration and opportunity
* Take their open, searching personality into account


## __Career Pragmatists__: 21%(USM 13%)

These students are looking for immediate ROI. They are highly sensitive to affordability, and are looking for the job right away. They are not necessarily focused on career.

__The Opening Conversation__

* Demonstrate an immediate return on investment 
* They want an affordable education in a supportive community setting that leads to an immediate job
* They may need a flexible program to accommodate a need to work

__Potential Blind Spots__

* They may overlook the importance of academics
* They don’t need to hear about rigor or prestige
* Educate them on the contribution of academic experiences to their career

__Opportunities for Support__

* Work and affordability issues could sidetrack them
* Introduce long-term benefits to career beyond the all-important first job  
* Provide strong academic advising
* Provide career advising to get the most out of their work experience




## __Experiential Interest__: 19% (USM 8%)

These students desire a career and want to get hands on with internships and employment. They are also highly sensitive to affordability.

__The Opening Conversation__

* Speak to experiential learning opportunities that lead to career-focused outcomes
* They will appreciate clearly laid out programs and degree plans
* Remember that they are highly sensitive to affordability 

__Potential Blind Spots__

* They consider academic coursework secondary 
* They aren’t paying much attention to the social aspects of college
* Work to heighten their understanding of the importance academic and social to success in college

__Opportunities for Support__

* They may run into trouble if they find themselves off their intended program path
* Help conscientious, but closed, students negotiate to another path if this arises



## __Social Focus__: 18% (USM 8%)

These students want to gain meaningful friendships (and a job would be nice too!). They want to engage in every connecting activity possible and the social environment is most critical to choice.

__The Opening Conversation__

* Showcase the defining aspects of your social environment
* Show how they can create lasting friendships 
* Support connections and social facility that drive success in the workplace

__Potential Blind Spots__

* They think they will get a good job after graduation almost by osmosis
* They aren’t very concerned about academics and career preparation 
* Instill an understanding of the importance of these key factors in success

__Opportunities for Support__

* Recognize a lesser degree of emotional stability and conscientiousness
* They may need more help getting on track with an academic and career plan 
* If social transition goes south, they are at high risk






# Other Findings

Below are some of the other findings available from the NRCCUA data downloads. 


```{r}
kable(trythis %>% group_by(`Application Status` = App.Application.Status) %>% summarise(Apps =  n())%>% arrange(desc(Apps)))
kable(trythis %>% group_by(State = State.Province) %>% summarise(Apps =  n())%>% arrange(desc(Apps)))
kable(trythis %>% group_by(County = County.Name) %>% summarise(Apps =  n())%>% arrange(desc(Apps)))
kable(trythis %>% group_by(Gender = Gender.x) %>% summarise(Apps =  n())%>% arrange(desc(Apps)))
kable(trythis %>% group_by(High.School.Name) %>% summarise(Apps =  n())%>% arrange(desc(Apps)))
kable(trythis %>% group_by(Specialization = Specialized.College.1) %>% summarise(Apps =  n())%>% arrange(desc(Apps)))
kable(trythis %>% group_by(`HS Track` = HS.Course.Track.1) %>% summarise(Apps =  n())%>% arrange(desc(Apps)))
kable(trythis %>% group_by(`College Activity` = College.Activity.1) %>% summarise(Apps =  n()) %>% arrange(desc(Apps)))
kable(trythis %>% group_by(`College Activity2` =College.Activity.2) %>% summarise(Apps =  n()) %>% arrange(desc(Apps)))
kable(trythis %>% group_by(`College Sport` = College.Sport.1) %>% summarise(Apps =  n()) %>% arrange(desc(Apps)))
kable(trythis %>% group_by(`Academic Interest`=Academic.Interest.1) %>% summarise(Apps =  n()) %>% arrange(desc(Apps)))
kable(trythis %>% group_by(`Career Interest` = Career.Interest.1) %>% summarise(Apps =  n()) %>% arrange(desc(Apps)))
```


# Conclusion

* Point 1


